Formalizing the Edmonds-Karp Algorithm

### 2016-03-02 paper/root.tex

\emph{\textbf{Proof.}} first observe that if $(u, v) \in E$, then $c_f(v, u) = f(u, v)$. Therefore, we have $f'(v,u) \leq c_f(v, u) = f(u, v)$, and hence
	\begin{align*}
	(f \uparrow f') (u, v) &= f(u, v) + f'(u, v) - f'(v, u)  && \text{(by definition of augment)} \\
	& \geq f(u, v) + f'(u, v) - f(v, u) && \text{(because $f'(v,u) \leq f(u, v)$)} \\
	& = f'(u, v) \\
	& \geq 0.
	\end{align*}
In addition,
	\begin{align*}
	(f \uparrow f') (u, v) &= f(u, v) + f'(u, v) - f'(v, u)  && \text{(by definition of augment)} \\
	& \leq f(u, v) + f'(u, v) && \text{(because flows are nonnegative)} \\
	& \leq f(u, v) + c_f(u, v) &&  \text{(capacity constraint)} \\
	& = f'(u, v) + c(u, v) - f(u, v) && \text{(definition of $c_f$)} \\
	& = c (u, v).
	\end{align*}

>>>>

\emph{\textbf{Proof.}} first observe that if $(u, v) \in E$, then $c_f(v, u) = f(u, v)$. Therefore, we have $f'(v,u) \leq c_f(v, u) = f(u, v)$, and hence
	\begin{align*}
	(f \uparrow f') (u, v) &= f(u, v) + f'(u, v) - f'(v, u)  && \text{(by definition of augment)} \\
	& \geq f(u, v) + f'(u, v) - f(v, u) && \text{(because $f'(v,u) \leq f(u, v)$)} \\
	& = f'(u, v) \\
	& \geq 0.
	\end{align*}
In addition,
	\begin{align*}
	(f \uparrow f') (u, v) &= f(u, v) + f'(u, v) - f'(v, u)  && \text{(by definition of augment)} \\
	& \leq f(u, v) + f'(u, v) && \text{(because flows are nonnegative)} \\
	& \leq f(u, v) + c_f(u, v) &&  \text{(capacity constraint)} \\
	& = f(u, v) + c(u, v) - f(u, v) && \text{(definition of $c_f$)} \\
	& = c (u, v).
	\end{align*}
